Predicting Donald Trump's win

### 2020-11-02 outputs/paper/paper.Rmd
Added model switch

where the x values represent age groups and y values represent education levels.

@@

```{r res1,fig.cap = "Voting Patterns according to education levels",echo = FALSE, fig.width=8, fig.height=2}
prediction_data <- read.csv("../cleaned data/prediction.csv")
prediction_data %>% 
ggplot()+ geom_bar(aes(x=Predicted_vote,fill=educ_level))+labs(x = "Predicted Vote", y = "Number of People",fill="Education Levels")

@@

```{r res2,fig.cap = "Voting Patterns according to age groups",echo = FALSE, fig.width=8, fig.height=2}
prediction_data %>% 
  ggplot()+ geom_bar(aes(x=Predicted_vote,fill=age_groups))+labs(x = "Predicted Vote", y = "Number of People",fill="age groups")
```

>>>>

where the x values represent age groups and y values represent education levels. $x_i$ is 1 when that sample contain a particular age group category while $y_i$ is 1 when there is a particular level of education category. the value is 0 otherwise.

```{r table2, echo = FALSE}
# table of xi or yi values so that we know which value is 1 or 0
tab_values<-as.matrix(rbind(cbind("x1","31-45 years old"),cbind("x2","46-65 years old"),cbind("x3","Above 65 years old"),cbind("y1","Doctorate Degree"),cbind("y2","Grade School"),cbind("y3","Master's or above bachelor's degree")))

kbl(tab_values,caption = 'switch for equation 2',col.names = c("","Categories"))%>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

If the age group is 18-30 years old, x1,x2,x3 is all 0. If the level of education is College, y1,y2,y3 is all 0. those are the baseline for the model.

@@

```{r res1,fig.cap = "Voting Patterns according to education levels",echo = FALSE, fig.width=8, fig.height=2}
prediction_data <- read.csv("../cleaned data/prediction.csv")
prediction_data %>% 
ggplot()+ geom_bar(aes(x=Predicted_vote,fill=educ_level),colour="black")+labs(x = "Predicted Vote", y = "Number of People",fill="Education Levels")

@@

```{r res2,fig.cap = "Voting Patterns according to age groups",echo = FALSE, fig.width=8, fig.height=2}
prediction_data %>% 
  ggplot()+ geom_bar(aes(x=Predicted_vote,fill=age_groups),colour="black")+labs(x = "Predicted Vote", y = "Number of People",fill="age groups")
```
